animbook: Visualizing Changes in Performance Measures and Demographic Affiliations using Animation

### 2025-07-08 response_to_review.qmd

## Code

*Usability:*

- *Page 6: it states that users can specify breaks on a 0 to 1 scale. Is there a reason why users can't provide breaks on the raw data scale and have the function transforms the values to fit the 0 and 1 scale?*

Response: In the function, before separating the observation into groups, it will go through normalization (the data scale will be between 0 and 1). If we implement the raw data scale, it would require redesigning the function, as it would have to be able to distinguish between normalization and raw data scale. ??? is this too long?

@@

- *Page 8: could the last_plot() function be used by default so that users don't have to save the plot into a ggplot2 object?*

Response: It should work by default.

- *In the wallaby plot, the applicable points move from all categories to a single category (or vice versa). Is there a way to choose which single category gets used?*

Response: Yes, we have made it clearer in the arguments description and on page 10.

### 2025-07-08 animbook-journal.Rmd
reviewer 2 other comments section

  The arguments for the `anim_prep()` and `anim_prep_cat()` functions are listed in Tables `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{tab:tbl-num-la}','\\@ref(tab:tbl-num)'))` and `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{tab:tbl-cat-la}','\\@ref(tab:tbl-cat)'))` respectively. The `data`, `id`, `values`, and `time` arguments are required for both functions. The `ncat`, `breaks`, `group_scaling`, and `scaling` arguments are for the user to customize the data scaling calculation in the `anim_prep()` function. In the `anim_prep_cat` function, the users can customize the order of the category to be shown on the y-axis using the `order` argument. Then, for further customization regarding how the final visualization looks. The `group`, `label`, and `time_dependent` arguments can be adjusted.

  The `time_dependent` argument provides the user flexibility to choose whether points will start simultaneously (`time_dependent = TRUE`) or randomly (`time_dependent = FALSE`). The challenge with points starting at the same time is the formation of point clusters, making it difficult to track individual points. Allowing for the random starting time makes point tracking simpler. The starting times for the points are generated using the `runif()` function, where the `max` argument can be adjusted using the `width` parameter in the plotting function.

@@

@@

description2 <- c("The categorized data returned from the prep function.",
                  "The vector of the palette used by the function to supply the color to each group.",
                  "The vector of the palette used by the function to supply the color to the shaded area.",
                  "The choice of method used to create and display the plot, either gganimate or plotly. Default is gganimate.",
                  "Should the observations entered the visualization at the same time. Default is FALSE",
                  "A character string specifying the variable used for subsetting the data. The \"top\" and \"bottom\" strings can also be used in this argument. Default is \"top\".",
                  "The choice of relationship for the values to display on the plot, either \"one_many.\" or \"many_one\". Default is \"one_many\".",
                  "The number of points the users want for the wallaby plot. Default is NULL, which is the number of points equal to the original.",
                  "The proportion of the area occupied by the observations in the shaded areas. Default is 0.6.",
                  "The distance between the first and last observation in the animation. Default is 50.",
                  "The point size. Default is 2.",
                  "The opacity of the proportional shaded areas. Default is 0.1.")

@@

Figure \@ref(fig:top-many) shows the flexibility to use various options, such as `subset` or `relation`, to customize the plot appearance. Here `subset = "top"` is used to specify category A for the final time point, and `relation = "many_one"` is used to specify that all categories flowing into A at time point 2 are shown.

@@

Using `subset = "B"` will only show the point for a single category as shown in Figure \@ref(fig:b-many).

@@

  In Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:osiris-figure}','\\@ref(fig:osiris-gif)'))`, the focus is placed on companies that exited the market in 2018 that were in the market at some point since 2006. The gray regions show the proportion of companies in each of the categories in 2006 on the left that exited the market by 2018. (explain the difference in proportion and not listed companies). In 2006, the companies represented by points, colored by country, were in one of the quartiles or "Not listed" category. All the companies in the Top 25% were US companies. Any Japanese companies in the Top 25% in 2006 did not exit the market (Not listed). It is worth noting that there are actually none of the Japanese companies in the Top 25% in 2006. It is also interesting that the larger proportion of the companies in the Top 25% are getting de-listed, and the lower the quartiles, the less likely that the companies will exit the market.

@@

  From Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:voter-figure}','\\@ref(fig:voter-gif)'))`, it reveals an intriguing pattern where individuals who identified their gender as 'others' have shifted their voting preference from the Liberal Party, the leading party in 2006, to the Greens Party. This change in behavior could be linked to the Green Party's "A FAIRER, MORE EQUAL COMMUNITY" campaign, which advocates for full equality under the law and communities for LGBTIQ+ individuals.

  According to the survey (@lgbtiq), the Greens Party provided a detailed response to all nine priority areas that focus on changing systems and addressing health and well-being disparities among LGBTIQ+ communities. However, the Labor Party only gives a broad statement of commitment to a range of LGBTIQ+ and human rights issues. This includes working with LGBTIQ+ Australians and advocates to ensure equality before the law and full access to Medicare.

>>>>

  The arguments for the `anim_prep()` and `anim_prep_cat()` functions are listed in Tables `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{tab:tbl-num-la}','\\@ref(tab:tbl-num)'))` and `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{tab:tbl-cat-la}','\\@ref(tab:tbl-cat)'))` respectively. The `data`, `id`, `values`, and `time` arguments are required for both functions. The `ncat`, `breaks`, `group_scaling`, and `scaling` arguments are for the user to customize the data scaling calculation in the `anim_prep()` function. In the `anim_prep_cat` function, the users can customize the order of the category to be shown on the y-axis using the `order` argument. Then, for further customization regarding how the final visualization looks. The `group`, `label`, and `time_dependent` arguments can be adjusted. The `time_dependent` argument will be further discussed in the next section.

@@

  The user can further use the `time_dependent` argument to choose whether points will start simultaneously (`time_dependent = TRUE`) or randomly (`time_dependent = FALSE`). The challenge with points starting at the same time is the formation of point clusters, making it difficult to track individual points. Allowing for the random starting time makes point tracking simpler. The starting times for the points are generated using the `runif()` function, where the `max` argument can be adjusted using the `width` parameter in the plotting function.

@@

description2 <- c("The categorized data returned from the prep function.",
                  "The vector of the palette used by the function to supply the color to each group.",
                  "The vector of the palette used by the function to supply the color to the shaded area.",
                  "The choice of method used to create and display the plot, either gganimate or plotly. Default is gganimate.",
                  "Should the observations entered the visualization at the same time. Default is FALSE",
                  "A character string specifying the label used for subsetting the data. The \"top\" and \"bottom\" strings can also be used in this argument. Default is \"top\".",
                  "The choice of relationship for the values to display on the plot, either \"one_many.\" or \"many_one\". Default is \"one_many\".",
                  "The number of points the users want for the wallaby plot. Default is NULL, which is the number of points equal to the original.",
                  "The proportion of the area occupied by the observations in the shaded areas. Default is 0.6.",
                  "The distance between the first and last observation in the animation. Default is 50.",
                  "The point size. Default is 2.",
                  "The opacity of the proportional shaded areas. Default is 0.1.")

@@

Figure \@ref(fig:top-many) shows the flexibility to use various options, such as `subset` or `relation`, to customize the plot appearance. Here `subset = "top"` is used to specify category A for the final time point, and `relation = "many_one"` is used to specify that all categories flowing into A at time point 2 are shown. However, if category B is the focusing point, setting `subset = "B"` will also allow for a choice of category to be shown as in Figure \@ref(fig:b-many).

@@

@@

  In Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:osiris-figure}','\\@ref(fig:osiris-gif)'))`, the focus is placed on companies that exited the market in 2018 that were in the market at some point since 2006. The gray regions show the proportion of companies in each of the categories in 2006 on the left that exited the market by 2018. In 2006, the companies represented by points, colored by country, were in one of the quartiles or "Not listed" category. All the companies in the Top 25% were US companies. Any Japanese companies in the Top 25% in 2006 did not exit the market (Not listed). It is worth noting that there are actually none of the Japanese companies in the Top 25% in 2006. It is also interesting that the larger proportion of the companies in the Top 25% are getting de-listed, and the lower the quartiles, the less likely that the companies will exit the market.

@@

  From Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:voter-figure}','\\@ref(fig:voter-gif)'))`, it reveals an intriguing pattern where individuals who identified their gender as 'others' have shifted their voting preference from the Liberal Party, the leading party in 2006, to the Greens Party. This change in behavior could be linked to the Green Party's "A FAIRER, MORE EQUAL COMMUNITY" campaign, which advocates for full equality under the law and communities for LGBTIQ+ individuals. According to the survey (@lgbtiq), the Greens Party provided a detailed response to all nine priority areas that focus on changing systems and addressing health and well-being disparities among LGBTIQ+ communities. However, the Labor Party only gives a broad statement of commitment to a range of LGBTIQ+ and human rights issues. This includes working with LGBTIQ+ Australians and advocates to ensure equality before the law and full access to Medicare.

### 2025-07-08 animbook-journal.tex
reviewer 2 other comments section

\hypertarget{intro}{%
\section{Introduction}\label{intro}}

@@

\hypertarget{NYTvis}{%
\section{Explanation of the New York Times visualization}\label{NYTvis}}

@@

\hypertarget{data}{%
\section{Data}\label{data}}

@@

\hypertarget{animation}{%
\section{Animation tools}\label{animation}}

@@

\hypertarget{design}{%
\section{Visualization design}\label{design}}

@@

\hypertarget{software}{%
\section{Software}\label{software}}

\hypertarget{installation}{%
\subsection{Installation}\label{installation}}

@@

\hypertarget{data-pre-processing}{%
\subsubsection{Data pre-processing}\label{data-pre-processing}}

@@

The arguments for the \texttt{anim\_prep()} and \texttt{anim\_prep\_cat()} functions are listed in Tables \ref{tab:tbl-num-la} and \ref{tab:tbl-cat-la} respectively. The \texttt{data}, \texttt{id}, \texttt{values}, and \texttt{time} arguments are required for both functions. The \texttt{ncat}, \texttt{breaks}, \texttt{group\_scaling}, and \texttt{scaling} arguments are for the user to customize the data scaling calculation in the \texttt{anim\_prep()} function. In the \texttt{anim\_prep\_cat} function, the users can customize the order of the category to be shown on the y-axis using the \texttt{order} argument. Then, for further customization regarding how the final visualization looks. The \texttt{group}, \texttt{label}, and \texttt{time\_dependent} arguments can be adjusted.

The \texttt{time\_dependent} argument provides the user flexibility to choose whether points will start simultaneously (\texttt{time\_dependent\ =\ TRUE}) or randomly (\texttt{time\_dependent\ =\ FALSE}). The challenge with points starting at the same time is the formation of point clusters, making it difficult to track individual points. Allowing for the random starting time makes point tracking simpler. The starting times for the points are generated using the \texttt{runif()} function, where the \texttt{max} argument can be adjusted using the \texttt{width} parameter in the plotting function.

\hypertarget{plotting-function}{%
\subsubsection{Plotting function}\label{plotting-function}}

@@

@@

\caption{\label{tab:unnamed-chunk-9}The arguments for the wallaby\_plot function.}
\centering
\begin{tabular}[t]{l|>{\raggedright\arraybackslash}p{30em}}
\hline
Argument & Description\\
\hline
data & The categorized data returned from the prep function.\\
\hline
group\_palette & The vector of the palette used by the function to supply the color to each group.\\
\hline
shade\_palette & The vector of the palette used by the function to supply the color to the shaded area.\\
\hline
rendering & The choice of method used to create and display the plot, either gganimate or plotly. Default is gganimate.\\
\hline
time\_dependent & Should the observations entered the visualization at the same time. Default is FALSE\\
\hline
subset & A character string specifying the variable used for subsetting the data. The "top" and "bottom" strings can also be used in this argument. Default is "top".\\
\hline
relation & The choice of relationship for the values to display on the plot, either "one\_many." or "many\_one". Default is "one\_many".\\
\hline
total\_point & The number of points the users want for the wallaby plot. Default is NULL, which is the number of points equal to the original.\\
\hline
height & The proportion of the area occupied by the observations in the shaded areas. Default is 0.6.\\
\hline
width & The distance between the first and last observation in the animation. Default is 50.\\
\hline
size & The point size. Default is 2.\\
\hline
alpha & The opacity of the proportional shaded areas. Default is 0.1.\\
\hline
\end{tabular}
\end{table}

\hypertarget{animating-function}{%
\subsubsection{Animating function}\label{animating-function}}

@@

\hypertarget{example-usage}{%
\subsection{Example usage}\label{example-usage}}

@@

Figure \ref{fig:top-many} shows the flexibility to use various options, such as \texttt{subset} or \texttt{relation}, to customize the plot appearance. Here \texttt{subset\ =\ "top"} is used to specify category A for the final time point, and \texttt{relation\ =\ "many\_one"} is used to specify that all categories flowing into A at time point 2 are shown.

@@

Using \texttt{subset\ =\ "B"} will only show the point for a single category as shown in Figure \ref{fig:b-many}.

@@

\hypertarget{applications}{%
\section{Applications}\label{applications}}

@@

\hypertarget{accounting-database-osiris}{%
\subsection{Accounting database: osiris}\label{accounting-database-osiris}}

@@

In Figure \ref{fig:osiris-figure}, the focus is placed on companies that exited the market in 2018 that were in the market at some point since 2006. The gray regions show the proportion of companies in each of the categories in 2006 on the left that exited the market by 2018. (explain the difference in proportion and not listed companies). In 2006, the companies represented by points, colored by country, were in one of the quartiles or ``Not listed'' category. All the companies in the Top 25\% were US companies. Any Japanese companies in the Top 25\% in 2006 did not exit the market (Not listed). It is worth noting that there are actually none of the Japanese companies in the Top 25\% in 2006. It is also interesting that the larger proportion of the companies in the Top 25\% are getting de-listed, and the lower the quartiles, the less likely that the companies will exit the market.

@@

\hypertarget{voter-behavior}{%
\subsection{Voter behavior}\label{voter-behavior}}

@@

From Figure \ref{fig:voter-figure}, it reveals an intriguing pattern where individuals who identified their gender as `others' have shifted their voting preference from the Liberal Party, the leading party in 2006, to the Greens Party. This change in behavior could be linked to the Green Party's ``A FAIRER, MORE EQUAL COMMUNITY'' campaign, which advocates for full equality under the law and communities for LGBTIQ+ individuals.

According to the survey (\citet{lgbtiq}), the Greens Party provided a detailed response to all nine priority areas that focus on changing systems and addressing health and well-being disparities among LGBTIQ+ communities. However, the Labor Party only gives a broad statement of commitment to a range of LGBTIQ+ and human rights issues. This includes working with LGBTIQ+ Australians and advocates to ensure equality before the law and full access to Medicare.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

@@

\hypertarget{acknowledgements}{%
\section*{Acknowledgements}\label{acknowledgements}}
\addcontentsline{toc}{section}{Acknowledgements}

>>>>

\section{Introduction}\label{intro}

@@

\section{Explanation of the New York Times visualization}\label{NYTvis}

@@

\section{Data}\label{data}

@@

\section{Animation tools}\label{animation}

@@

\section{Visualization design}\label{design}

@@

\section{Software}\label{software}

\subsection{Installation}\label{installation}

@@

\subsubsection{Data pre-processing}\label{data-pre-processing}

@@

The arguments for the \texttt{anim\_prep()} and \texttt{anim\_prep\_cat()} functions are listed in Tables \ref{tab:tbl-num-la} and \ref{tab:tbl-cat-la} respectively. The \texttt{data}, \texttt{id}, \texttt{values}, and \texttt{time} arguments are required for both functions. The \texttt{ncat}, \texttt{breaks}, \texttt{group\_scaling}, and \texttt{scaling} arguments are for the user to customize the data scaling calculation in the \texttt{anim\_prep()} function. In the \texttt{anim\_prep\_cat} function, the users can customize the order of the category to be shown on the y-axis using the \texttt{order} argument. Then, for further customization regarding how the final visualization looks. The \texttt{group}, \texttt{label}, and \texttt{time\_dependent} arguments can be adjusted. The \texttt{time\_dependent} argument will be further discussed in the next section.

\subsubsection{Plotting function}\label{plotting-function}

@@

The user can further use the \texttt{time\_dependent} argument to choose whether points will start simultaneously (\texttt{time\_dependent\ =\ TRUE}) or randomly (\texttt{time\_dependent\ =\ FALSE}). The challenge with points starting at the same time is the formation of point clusters, making it difficult to track individual points. Allowing for the random starting time makes point tracking simpler. The starting times for the points are generated using the \texttt{runif()} function, where the \texttt{max} argument can be adjusted using the \texttt{width} parameter in the plotting function.

@@

\caption{\label{tab:unnamed-chunk-8}The arguments for the wallaby\_plot function.}
\centering
\begin{tabular}[t]{l|>{\raggedright\arraybackslash}p{30em}}
\hline
Argument & Description\\
\hline
data & The categorized data returned from the prep function.\\
\hline
group\_palette & The vector of the palette used by the function to supply the color to each group.\\
\hline
shade\_palette & The vector of the palette used by the function to supply the color to the shaded area.\\
\hline
rendering & The choice of method used to create and display the plot, either gganimate or plotly. Default is gganimate.\\
\hline
time\_dependent & Should the observations entered the visualization at the same time. Default is FALSE\\
\hline
subset & A character string specifying the label used for subsetting the data. The "top" and "bottom" strings can also be used in this argument. Default is "top".\\
\hline
relation & The choice of relationship for the values to display on the plot, either "one\_many." or "many\_one". Default is "one\_many".\\
\hline
total\_point & The number of points the users want for the wallaby plot. Default is NULL, which is the number of points equal to the original.\\
\hline
height & The proportion of the area occupied by the observations in the shaded areas. Default is 0.6.\\
\hline
width & The distance between the first and last observation in the animation. Default is 50.\\
\hline
size & The point size. Default is 2.\\
\hline
alpha & The opacity of the proportional shaded areas. Default is 0.1.\\
\hline
\end{tabular}
\end{table}

\subsubsection{Animating function}\label{animating-function}

@@

\subsection{Example usage}\label{example-usage}

@@

Figure \ref{fig:top-many} shows the flexibility to use various options, such as \texttt{subset} or \texttt{relation}, to customize the plot appearance. Here \texttt{subset\ =\ "top"} is used to specify category A for the final time point, and \texttt{relation\ =\ "many\_one"} is used to specify that all categories flowing into A at time point 2 are shown. However, if category B is the focusing point, setting \texttt{subset\ =\ "B"} will also allow for a choice of category to be shown as in Figure \ref{fig:b-many}.

@@

@@

\section{Applications}\label{applications}

@@

\subsection{Accounting database: osiris}\label{accounting-database-osiris}

@@

In Figure \ref{fig:osiris-figure}, the focus is placed on companies that exited the market in 2018 that were in the market at some point since 2006. The gray regions show the proportion of companies in each of the categories in 2006 on the left that exited the market by 2018. In 2006, the companies represented by points, colored by country, were in one of the quartiles or ``Not listed'' category. All the companies in the Top 25\% were US companies. Any Japanese companies in the Top 25\% in 2006 did not exit the market (Not listed). It is worth noting that there are actually none of the Japanese companies in the Top 25\% in 2006. It is also interesting that the larger proportion of the companies in the Top 25\% are getting de-listed, and the lower the quartiles, the less likely that the companies will exit the market.

@@

\subsection{Voter behavior}\label{voter-behavior}

@@

From Figure \ref{fig:voter-figure}, it reveals an intriguing pattern where individuals who identified their gender as `others' have shifted their voting preference from the Liberal Party, the leading party in 2006, to the Greens Party. This change in behavior could be linked to the Green Party's ``A FAIRER, MORE EQUAL COMMUNITY'' campaign, which advocates for full equality under the law and communities for LGBTIQ+ individuals. According to the survey (\citet{lgbtiq}), the Greens Party provided a detailed response to all nine priority areas that focus on changing systems and addressing health and well-being disparities among LGBTIQ+ communities. However, the Labor Party only gives a broad statement of commitment to a range of LGBTIQ+ and human rights issues. This includes working with LGBTIQ+ Australians and advocates to ensure equality before the law and full access to Medicare.

\section{Discussion}\label{discussion}

@@

\section*{Acknowledgements}\label{acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}
